Digital Addiction

### 2024-02-13 output/paper.qmd
paper

>>>>

#Data
The authors in their experiment mainly adopted the standardized measures from the subjective well-being literature, where the respondents were required to answer the following seven questions of a questionnaire after conducting different groups of rules each week, Over the last three weeks," with a matrix of seven questions : - "...I was a happy person." - "...I was satisfied with my I felt anxious." "...I felt depressed." "...I could concentrate on my life." - "...I could concentrate on what I was doing." - "...I was easily distracted." - "...I was easily distracted." - "... I slept well." Based on the different responses it is possible to categorize and collect new data.
